{\huge Changes and trends in budburst and leaf flush across Europe and North America} \\A meta-analysis of local adaptation in spring phenology studies

### 2023-04-04 Docs/manuscript.Rnw
updated results

Overall, spring events were not related to provenance latitude (mean slope = \Sexpr{format(mean(northamerican_springpost_fitC_spring_lat),digits = 1)} $\pm$
\Sexpr{format(abs((quantile(northamerican_springpost_fitC_spring_lat, 0.95)-(quantile(northamerican_springpost_fitC_spring_lat, 0.05)))*0.5), digits = 2)}) or MAT (mean slope = \Sexpr{format(mean(northamerican_springpost_fitC_spring_mat),digits = 1)} $\pm$
  \Sexpr{format(abs((quantile(northamerican_springpost_fitC_spring_mat, 0.95)-(quantile(northamerican_springpost_fitC_spring_mat, 0.05)))*0.5), digits = 2)}) in North America. \todo{add figure here}  Spring events advanced slightly with provenance latitude (mean slope = \Sexpr{format(mean(european_springpost_fitC_spring_lat),digits = 1)} $\pm$
  \Sexpr{format(abs((quantile(european_springpost_fitC_spring_lat, 0.95)-(quantile(european_springpost_fitC_spring_lat, 0.05)))*0.5), digits = 2)}) and MAT (mean slope = \Sexpr{format(mean(european_springpost_fitC_spring_mat),digits = 1)} $\pm$
  \Sexpr{format(abs((quantile(european_springpost_fitC_spring_mat, 0.95)-(quantile(european_springpost_fitC_spring_mat, 0.05)))*0.5), digits = 2)}) in Europe, meaning spring events are slightly earlier where provenance MAT is lower (i.e., higher, more northern latitudes)(Fig. \ref{figure:springfall_latmat} \& Supplement Table. \ref{supplement-table:model_sf_lat}). Results were similar using other distance metrics in lieu of latitude (see Supplement Fig.\ref{supplement-figure:lat_distance} for results using the absolute value of the distance and the spherical distance difference between provenance and garden latitude).

>>>>

Overall, spring events were not related to provenance latitude (\Sexpr{format(mean(northamerican_springpost_fitC_spring_lat),digits = 1)} [\Sexpr{format(quantile(northamerican_springpost_fitC_spring_lat, 0.05), digits = 1)}-\Sexpr{format(quantile(northamerican_springpost_fitC_spring_lat, 0.95), digits = 2)}]) or MAT (\Sexpr{format(mean(northamerican_springpost_fitC_spring_mat),digits = 1)} [\Sexpr{format(quantile(northamerican_springpost_fitC_spring_mat, 0.05), digits = 2)}-\Sexpr{format(quantile(northamerican_springpost_fitC_spring_mat, 0.95), digits = 2)}]) in North America. \todo{add figure here} Spring events advanced slightly with provenance latitude (\Sexpr{format(mean(european_springpost_fitC_spring_lat),digits = 1)} [\Sexpr{format(quantile(european_springpost_fitC_spring_lat, 0.05), digits = 2)}-\Sexpr{format(quantile(european_springpost_fitC_spring_lat, 0.95), digits = 2)}]) and MAT (\Sexpr{format(mean(european_springpost_fitC_spring_mat),digits = 1)} [\Sexpr{format(quantile(european_springpost_fitC_spring_mat, 0.05), digits = 2)}-\Sexpr{format(quantile(european_springpost_fitC_spring_mat, 0.95), digits = 2)}]) in Europe, meaning spring events are slightly earlier where provenance MAT is lower (i.e., higher, more northern latitudes)(Fig. \ref{figure:springfall_latmat} \& Supplement Table. \ref{supplement-table:model_sf_lat}), though uncertainty intervals strongly overlapped zero. Results were similar using other distance metrics in lieu of latitude (see Supplement Fig.\ref{supplement-figure:lat_distance} for results using the absolute value of the distance and the spherical distance difference between provenance and garden latitude).

### 2023-04-04 Docs/manuscript.tex
updated results

Overall, spring events were not related to provenance latitude (mean slope = 0.1 $\pm$
0.16) or MAT (mean slope = -0.09 $\pm$
  0.27) in North America. \todo{add figure here}  Spring events advanced slightly with provenance latitude (mean slope = 0.1 $\pm$
  0.33) and MAT (mean slope = -0.2 $\pm$
  0.39) in Europe, meaning spring events are slightly earlier where provenance MAT is lower (i.e., higher, more northern latitudes)(Fig. \ref{figure:springfall_latmat} \& Supplement Table. \ref{supplement-table:model_sf_lat}). Results were similar using other distance metrics in lieu of latitude (see Supplement Fig.\ref{supplement-figure:lat_distance} for results using the absolute value of the distance and the spherical distance difference between provenance and garden latitude).

>>>>

Overall, spring events were not related to provenance latitude (0.1 [-0.06-0.26]) or MAT (-0.09 [-0.36-0.18]) in North America. \todo{add figure here} Spring events advanced slightly with provenance latitude (0.1 [-0.23-0.42]) and MAT (-0.2 [-0.55-0.23]) in Europe, meaning spring events are slightly earlier where provenance MAT is lower (i.e., higher, more northern latitudes)(Fig. \ref{figure:springfall_latmat} \& Supplement Table. \ref{supplement-table:model_sf_lat}), though uncertainty intervals strongly overlapped zero. Results were similar using other distance metrics in lieu of latitude (see Supplement Fig.\ref{supplement-figure:lat_distance} for results using the absolute value of the distance and the spherical distance difference between provenance and garden latitude).
